--- 
title: "FSS RDM Pages"
author: "FSW Data Steward"
date: '`r format(Sys.time(), "%d %B %Y")`'
site: bookdown::bookdown_site
documentclass: book
description: |
  These are the RDM Pages for the faculty of Social Sciences.
url: "https://vu-fss.github.io/rdm/"
github-repo: "/vu-fss/rdm"
---


```{r setup, include=FALSE}

library(tidyverse)
library(kableExtra)
library(stringr)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center")
Sys.setlocale("LC_TIME", "English")
local({r <- getOption("repos")
       r["CRAN"] <- "https://cloud.r-project.org" 
       options(repos=r)
})

display_more_resources <- T

more_resources <- 
"## FSS RDM Resources
- [Information when starting a new project][fss-getting-started]
- [FSS RDM Guidelines][fss-guidelines-rdm]
- [Data organization][fss-guidelines-organization]
- [Data archiving][fss-guidelines-archiving]
- [RDM FAQ][fss-rdm-faq]
- [Overview of RDM Tools ][fss-rdm-tools]
"

my_list <- list(a = 1, b = 2)

print_more_resources <- function(){
  if (display_more_resources){
    cat(more_resources)
  }
}

```

# Index

This web site contains the latest draft versions of the Research Office's pages on
Research Data Management. The current "official" versions of these pages can be accessed through
the [Social Sciences Getting Started page][fss-getting-started].

## Table of contents

- **Support throughout the Research Cycle**
  1. **Plan & Design**
    - [Content for proposals: Ethics, Privacy, RDM (Koen)](#proposal-content-rdm)
  2. **Starting a new project (Time to Grant)**
    - [Ethics, Data Management and Privacy for new projects](#new-rdm)
  3. **Managing ongoing projects**
    - [Organizing your research data (Koen)](#ongoing-rdm)
  4. **Publishing, and Impact**
    - [Archiving and/or publishing data (Koen)](#completed-rdm)
- **Knowledge and Guidelines**
  - [Templates](#templates)
  - RDM
    - [Data Management Policy](#rdm-policy)
    - [RDM FAQ](#rdm-faq)
    - [RDM Tools](#rdm-tools)
    - [A Guide to FAIR data](#rdm-fair)

<!---
load links from external file-
-->
```{r results="asis",echo = FALSE, message=F,warning=F}
cat(readLines('links.rmd'), sep = '\n')
```